Finch: Sparse and Structured Array Programming with Control Flow

### 2024-04-05 sections/eval/spmv.tex
cool

@@

  \begin{table}[htbp]
      \scriptsize
      \centering
      \vspace{-12pt}
      \caption{SpMV Tensor Formats}
      \vspace{-12pt}
      \label{spmv_tensor_formats}
      \begin{tabular}{|l|l|l|l|}
          \hline
          \textbf{Outer Level} & \textbf{Inner Level} & \textbf{Scalar Values} & \textbf{Style of Matrix}\\
          \hline
          \multirow{6}{*}{Dense} & \multirow{2}{*}{SparseList} & Element & sparse, real-valued matrices \\
          \cline{3-4} 
          & & Pattern & sparse, boolean-valued matrices \\
          \cline{2-4} 
          & SparseVBL & Element & real-valued matrices with blocked structure \\
          \cline{2-4}
          & SparseBand & Element & real-valued matrices with diagonal band \\
          \cline{2-4}
          & \multirow{2}{*}{SparsePoint} & Element & real-valued matrices with one value per row \\
          \cline{3-4} 
          & & Pattern & matrix with runs of true or false \\
          \hline 
      \end{tabular}
      \vspace{-8pt}
  \end{table}

@@

  \begin{figure}
      \includegraphics[width=\linewidth]{Spmv_annotated.png}
      \vspace{-18pt}
      \caption{Performance of SpMV by Finch format.}
      \label{fig:spmv_grouped}
      \footnotesize The performance displayed for Finch on each dataset is the fastest among the formats we tested. "R" indicates row-major implementation and "C" indicates column-major implementation in Finch. The baseline Finch format is unsymmetric Dense(SparseList(Element)).
  \end{figure}

>>>>

  \begin{wrapfigure}{r}{0.5\linewidth}
    \scriptsize
    \centering
    \vspace{-12pt}
    \vspace{-12pt}
    \begin{tabular}{|r|l|l|}
        \hline
        \textbf{Format} & \textbf{Style of Matrix}\\
        \hline
        \mintinline[fontsize=\scriptsize]{julia}{Dense(SparseList(Element(0.0)))} & real, sparse \\
        \mintinline[fontsize=\scriptsize]{julia}{Dense(SparseList(Pattern()))} & boolean, sparse \\
        \mintinline[fontsize=\scriptsize]{julia}{Dense(SparseVBL(Element(0.0)))} & real, blocked \\
        \mintinline[fontsize=\scriptsize]{julia}{Dense(SparseBand(Element(0.0)))} & real, banded \\
        %\mintinline{julia}{Dense(SparsePoint(Element(0.0)))} & real-valued matrices with one value per row \\
        %\mintinline{julia}{Dense(SparseRLE(Pattern(0.0)))} & matrix with runs of true or false \\
        \hline 
    \end{tabular}
    \caption{SpMV Tensor Formats}
    \label{spmv_tensor_formats}
    \vspace{-8pt}
  \end{wrapfigure}

@@

@@

  \begin{figure}
      \includegraphics[width=\linewidth]{Spmv_annotated.drawio.png}
      \vspace{-18pt}
      \caption{Performance of SpMV by Finch format.}
      \label{fig:spmv_grouped}
      \footnotesize The performance displayed for Finch on each dataset is the fastest among the formats we tested. Programs are from Figure~\ref{spmv_programs} and formats are from Figure~\ref{spmv_tensor_formats}. ``finch\_baseline'' is the faster of row major or column major ``SparseList''.
  \end{figure}
